Supplementary Information from:\\ \textit{Reconstructing the last known movements of one of Nature's giants}

### 2018-01-31 manuscript/revision/blue-whale-supplementary-v2.tex
Fig S4 legend edits

  \begin{figure}[!htbp]
    \centering
      \includegraphics[width=\linewidth]{figures/Figure-S4-regions-d13C.png}
      \caption{Alternative $\delta^{13}$C series arising from resident-only movement models restricting region to west UK/Irish shelf (Ireland), Norwegian/Barents Sea (Norway), Canaries/west Azores (Canaries), Mid Atlantic ridge (Mid-Atlantic), Cape Verde, and the Cape Verde/Mauritanian upwelling area over a simulated two year period with daily resolution and 30 replicate simulations for each region.} % check legend
      \label{figs4}
  \end{figure}

>>>>

  \begin{figure}[!htbp]
    \centering
      \includegraphics[width=\linewidth]{figures/Figure-S4-regions-d13C.png}
      \caption{$\delta^{13}$C values expected in baleen plates for whales simulated with resident foraging models (i.e. restricting movements to broad regions) (i)  Norwegian/Barents Sea (Norway), (ii) UK/Irish shelf (Ireland), (iii) Mid-Atlantic ridge (Mid-Atlantic), (D) Cape Verde/Mauritanean upwelling (Cape Verde), over a simulated two year period with daily resolution and 30 replicate simulations for each region. 
      Simulated $\delta^{13}$C values are six month moving average values for the time series of simulated plankton $\delta^{13}$C values in that location.}
      \label{figs4}
  \end{figure}
